%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Cover Letter
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage{lmodern} % Font
\usepackage{geometry} % For margins
\usepackage{hyperref} % For clickable links
\usepackage{fontawesome5} % For icons like phone, email

% Adjust page margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in,
}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\begin{document}

%------------------------------------------------
%   YOUR INFORMATION
%------------------------------------------------
\begin{center}
    \textbf{\LARGE Yashwanth Raj Tirupati}
    \vspace{4pt}
    
    \small
    \href{mailto:tyashwanth99@gmail.com}{ tyashwanth99@gmail.com }\textbar
     ~(937)-469-9700 \textbar
    \href{https://linkedin.com/in/yashwanthtirupati}{~ LinkedIn: yashwanthtirupati }\textbar 
    \href{https://github.com/proxiee}{~GitHub: proxiee }
\end{center}

\vspace{20pt}

%------------------------------------------------
%   RECIPIENT INFORMATION
%------------------------------------------------
\begin{flushleft}
    {{TODAYS_DATE}} \\
    \vspace{12pt}
    Hiring Manager \\
    DoorDash \\
    San Francisco, CA \\
\end{flushleft}

% \vspace{2pt}

%------------------------------------------------
%   SUBJECT LINE
%------------------------------------------------
\begin{flushleft}
\textbf{Subject: Application for Data Analyst, New Verticals Business Operations}
\end{flushleft}


% \vspace{2pt}

%------------------------------------------------
%   LETTER CONTENT
%------------------------------------------------
\begin{flushleft}
Dear Hiring Manager,

\vspace{12pt}

I am writing with great enthusiasm to apply for the Data Analyst, New Verticals Business Operations position. As a Master’s student in Computer Science, I have been following DoorDash’s ambitious expansion into retail, and the opportunity to help decode the "why" behind key business metrics is precisely the challenge I am seeking.

\vspace{12pt}

My background in software engineering is complemented by a dedicated focus on data science and statistical analysis through my academic and personal projects. My passion lies in transforming raw data into actionable insights, and I am adept at the structured, hypothesis-driven approach required to solve ambiguous problems.

\vspace{12pt}

The responsibilities in the job description align perfectly with my project experience. For instance, I have:

\begin{itemize}
    \item Developed a \textbf{Retail Customer Journey Analysis} project using cohort analysis in Python to segment users across retail categories, directly mirroring your need to analyze the customer journey for items in Household, Electronics, and Apparel.
    \item Built a full \textbf{A/B Testing Framework} using SQL and Python to evaluate promotional effectiveness, which resulted in a 12\% increase in conversion rates in a simulated environment.
    \item Conducted a \textbf{Time Series Analysis of Retail Sales}, developing a forecasting model that predicted future trends with 95\% accuracy to provide a "forward-looking outlook."
\end{itemize}

\vspace{2pt}

These projects demonstrate my proficiency with SQL, Python, Tableau, and the core statistical methods outlined in your requirements. I am confident in my ability to build sophisticated diagnostic tools and present clear, data-backed stories to help drive DoorDash's retail strategy forward. My resume provides further detail on my qualifications, and I am eager for the opportunity to discuss how my skills can be an asset to your team.

\vspace{20pt}

Sincerely, \\
% \vspace{15pt}
Yashwanth Raj Tirupati

\end{flushleft}

\end{document}
