
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1.0pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{\small#1} & \textit{\small #2} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}


\begin{center}
    \textbf{\Huge \scshape {\fontsize{15pt}{20pt}\selectfont Yashwanth Raj Tirupati}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (937)-469-9700 ~ \href{mailto:tyashwanth99@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tyashwanth99@gmail.com}} ~ 
    \href{https://linkedin.com/in/yashwanthtirupati}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/yashwanthtirupati}} ~ 
    \href{https://github.com/proxiee}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/proxiee}}
    \vspace{-8pt}
\end{center}


\section{{\fontsize{9pt}{20pt}\selectfont \textbf{SUMMARY}}}
\resumeSubHeadingListStart

\resumeItem{A highly motivated and results-oriented software engineer with 2+ years of experience in designing, developing, and deploying robust software systems. Proven ability to translate user requirements into technical specifications, collaborate effectively within Agile teams, and deliver high-quality solutions with a focus on efficiency and maintainability.  Expert in Java and Python, with a strong foundation in database fundamentals and experience working with cloud technologies like AWS and containerization platforms such as Docker and Kubernetes.}
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EDUCATION}}}
\resumeSubHeadingListStart
\resumeSubheading{University of Dayton}{\textbf{Dayton, Ohio, USA}}{M.S. in Computer Science}{Aug 2023 - May 2025}
\resumeItemListStart
\resumeItem{\textbf{Concentrations:} Autonomous Systems and Data Science}
\resumeItem{\textbf{GPA:} 3.41/4.00}
\resumeItem{\textbf{Related Coursework:} Data Structures \& Algorithms, Objects \& Design, Virtual Reality, Machine Learning, Artificial Intelligence, Object-Oriented Programming, Algorithm Design, Advanced Computer Vision.}
\resumeItemListEnd
\resumeSubheading{Jawaharlal Nehru Technological University}{\textbf{Hyderabad, Telangana, India}}{B.Tech. in Computer Science \& Engineering}{June 2018 - July 2022}
\resumeItemListStart
\resumeItem{\textbf{CGPA:} 7.3/10.00}
\resumeItem{\textbf{Related Coursework:} Operating Systems, Database Management Systems, Computer Networks, Discrete Mathematics, Web Technologies, Software Engineering.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{EXPERIENCE}}}
\resumeSubHeadingListStart
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Chennai, Tamil Nadu, India}}{Software Developer}{March 2023 - Aug 2023}
\resumeItemListStart
\resumeItem{Developed and deployed 5 full-stack features for enterprise-level systems using Spring Boot (Java) and React, resulting in a 15\% improvement in API response times and enhancing system scalability.}
\resumeItem{Collaborated with product stakeholders and an Agile team to translate user requirements into technical specifications, delivering robust solutions that met stringent performance and maintainability standards.}
\resumeItemListEnd
\resumeSubheading{Cognizant Technology Solutions}{\textbf{Chennai, Tamil Nadu, India}}{Programmer Analyst Intern}{March 2022-Sept 2022}
\resumeItemListStart
\resumeItem{Identified and resolved 100+ bugs in enterprise applications, leading to a 10\% reduction in reported issues and improved application stability for key modules.}
\resumeItem{Developed and implemented comprehensive technical documentation and automated testing procedures that increased code quality and reduced deployment risks.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{PROJECTS}}}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Enterprise-Grade Software System Enhancement using Microservices Architecture}}{\textit{Jan 2024-May 2025}}
\resumeItemListStart
\resumeItem{Designed and implemented a microservices architecture using Spring Boot and Docker, resulting in a 20\% increase in system throughput and improved scalability.}
\resumeItem{Developed RESTful APIs with comprehensive documentation and unit tests, ensuring seamless integration with existing systems and minimizing deployment risks.}
\resumeItemListEnd\vspace{-12pt}
\resumeProjectHeading{\textbf{High-Availability Data Pipeline using Kubernetes and Kafka}}{\textit{Jun 2024 - Present}}
\resumeItemListStart
\resumeItem{Architected and deployed a high-availability data pipeline using Kubernetes, Kafka, and PostgreSQL, achieving 99.99\% uptime and reducing data processing latency by 30\%.}
\resumeItem{Implemented robust monitoring and alerting systems to proactively identify and mitigate potential issues, improving overall system reliability and reducing downtime.}
\resumeItemListEnd\vspace{-12pt}
\resumeProjectHeading{\textbf{Secure and Scalable Cloud-Based Application using AWS}}{\textit{Sep 2023-Dec 2023}}
\resumeItemListStart
\resumeItem{Developed and deployed a secure and scalable cloud-based application on AWS using EC2, S3, and RDS, reducing infrastructure costs by 15\% while improving application performance.}
\resumeItem{Implemented robust security measures to protect sensitive data, adhering to industry best practices and ensuring compliance with relevant regulations.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-17pt}

\section{{\fontsize{9pt}{20pt}\selectfont \textbf{ACTIVITIES AND LEADERSHIP}}}
\resumeSubHeadingListStart
\resumeSubheading{University of Dayton}{\textbf{Dayton, Ohio, USA}}{}{}
\vspace{-17pt}
\resumeItemListStart
\resumeItem{Teaching Assitant, CPS 501 (Advanced Programming and Data Structures)} \hfill \textit{Jan 2024-Apr 2024}
\resumeItem{Secretary, Indian Student Association (100+ members)} \hfill \textit{Aug 2023-Apr 2024}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-18pt}

\section{\textbf{Skills}}
\resumeSubHeadingListStart
\resumeItem{\textbf{Languages:} Python, Java, C++, C, JavaScript, Kotlin}\vspace{-7pt}
\resumeItem{\textbf{Frontend:} HTML, CSS, ReactJS, AJAX}\vspace{-7pt}
\resumeItem{\textbf{Backend Frameworks:} SpringBoot, NodeJS}\vspace{-7pt}
\resumeItem{\textbf{Database:} MySQL, MongoDB, Postgres}\vspace{-7pt}
\resumeItem{\textbf{Automation:} Appium, Selenium, Cucumber BDD, Jenkins, JUnit}\vspace{-7pt}
\resumeItem{\textbf{AI \& ML:} PyTorch, TensorFlow, Jupyter, OpenCV, LLMs(GPT)}
\resumeSubHeadingListEnd
\vspace{-10pt}
\end{document}